\bf Drift Removal for Time Series Data Using Quantile Trend Filtering

### 2019-01-22 Manuscript/detrendify_JCGS.tex

@@

@@

	\begin{figure}
		\caption{Low cost sensor data before drift removal (top), after drift removal using windowed detrend with eBIC (middle), 
			and zoomed in on signal area (bottom). Horizontal lines represent signal thresholds.}
		\includegraphics[width = \linewidth]{Figures/uncorrected_data.png}
		\includegraphics[width = \linewidth]{Figures/corrected_data.png}
		\includegraphics[width = \linewidth]{Figures/corrected_zoom_data.png}
	\end{figure}

@@

	\includegraphics[width = \linewidth]{Figures/corrected_rugplot.png}

>>>>

	\begin{figure}
		\caption{Example of 3 co-located SPod PID sensor readings.}
		\includegraphics[width = \linewidth]{Figures/uncorrected_data.png}
	\end{figure}

@@

	We compared our detrend method with the eBIC criteria with the qsreg method on a subset of the real data since the qsreg method cannot handle all 15 hours simultaneously. We estimate the baseline trend using both the 5th and 10th quantiles and then classify the signal as any observation above the median plus 2.5 times the median absolute deviation after the baseline trend removal. We report both the confusion matrices and the normalized mutual information (NMI) score.

	\input{short_confusion_detrend.tex}

	\begin{figure}
		\caption{Rugplot showing locations of signal after baseline removal using detrendr estimate of 10th quantile.}
		\includegraphics[width = \linewidth]{Figures/corrected_rugplot.png}
	\end{figure}

	\input{NMI.tex}

@@

	\begin{figure}
		\caption{Low cost sensor data before drift removal (top), after drift removal using windowed detrend with eBIC (middle), 
			and zoomed in on signal area (bottom). Horizontal lines represent signal thresholds.}
		\includegraphics[width = \linewidth]{Figures/corrected_data.png}
		\includegraphics[width = \linewidth]{Figures/corrected_zoom_data.png}
	\end{figure}

@@
